%% start of file `template.tex'.
%% Copyright 2006-2010 Xavier Danaux (xdanaux@gmail.com).
%% Copyright 2010-2011 Mark Liu (markwayneliu@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[11pt,a4paper,sans]{moderncv}

\usepackage{verbatim}

% moderncv themes
\moderncvstyle{classic}
\moderncvcolor{blue}

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.8]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
%\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths


% personal data
\firstname{Md. Enamul}
\familyname{Hoque}
\address{22/2 Rebeca Monzil, Nibash-C, Al-Arafah A/E}{Modina
Market, Sylhet - 3100, Bangladesh}    % optional, remove the line if not wanted
\mobile{+880 1719 277759}                    % optional, remove the line if not wanted
\email{mjonyh-phy@sust.edu}                      % optional, remove the line if not wanted
%\email{mjonyh@gmail.com}
\homepage{https://sites.google.com/site/mjonyh}                % optional, remove the line if not wanted
\extrainfo{\url{http://github.com/mjonyh}} % optional, remove the line if not wanted

% to show numerical labels in the bibliography; only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{Education}
\cventry{Current}{PhD, Nonlinear Optics}{Shahjalal University of Science and Technology}{Sylhet - 3114, Bangladesh}{}{}
\cvline{Thesis:}{Enhancement of Second Harmonic Generation by Metallic Nanoparticles.}
\cvline{Advisors:}{\small Professor Yasmeen Haque and Professor Susanta Kumar Das}
\cventry{2010}{MS, Physics}{Shahjalal University of Science and Technology}{Sylhet - 3114, Bangladesh}{}{}
\cvline{Thesis:}{Analysis of $\alpha$-nucleus Potential for the Stripping Reaction of $ ^{60, 62, 64}Ni $.}
\cvline{Advisor:}{\small Professor Susanta Kumar Das}
\cvline{CGPA:}{3.74/4.00}
\cventry{2008}{BSc, Physics}{Shahjalal University of Science and Technology}{Sylhet - 3114, Bangladesh}{}{}
\cvline{Project:}{The Simple Harmonic Oscillator Potential, The Square Well Potential and Their Supersymmetric Potentials and Wavefunctions.}
\cvline{Advisor:}{\small Professor Susanta Kumar Das}
\cvline{CGPA:}{3.59/4.00}

\section{Experience}

\cventry{2015--Current}{Assistant Professor}{Department of Physics}{Shahjalal
University of Science and Technology, Sylhet - 3114}{Bangladesh}{Conducted
``Computational Physics I'' and ''Computation Physics II'' and MS Laboratory.}

\cventry{2013--2015}{Lecturer}{Department of Physics}{Shahjalal University of
Science and Technology}{Sylhet - 3114, Bangladesh}{I am teaching the course
    "Computational Physics I" and "Computational Physics II" in the last two
    semester of B.Sc in Physics at the department respectively. Both of the
    courses required to complete a project work on computation or simulation. I
    am also conducting the MS laboraty course which contain the physics
experiment and simulation. }

\cventry{2011--2014}{Web application developer, Founder Member}{IT Lab
Solutions}{Sylhet - 3100, Bangladesh}{}{The software farm, IT Lab Solutions
    (\url{http://www.itlabsolutions.com}), was founded to develop web
    application and research. Currently, the farm is collaborating with the
    Leading University, Sylhet  and the Metropolitan University, Sylhet for the
internship of the student of B.Sc. in Computer Science department. }

\cventry{2010--2012}{Lecturer}{North East Nursing Institute and College}{Sylhet
- 3100, Bangladesh}{}{I taught the physics part of the course "Physics and
    Chemistry in Nursing" which contain the fundamental physics with X-Ray,
Gamma-Ray, Ultra Sonic etc. }

\cventry{2009--2010}{Lecturer}{Sylhet Science College}{Sylhet - 3100,
Bangladesh}{}{I taught the physics course of higher secondary school level. I
also conducted the examination processes.}

\cventry{2010--2011}{Web application developer}{IFIX}{Sylhet - 3100,
Bangladesh}{}{I worked as a web application developer with PHP, CSS and MySQL
to develop website.}

% \section{Publications}
% \subsection{Journal Articles}
% \cvline{1.}{Ponkog K. Das, Manash K. Biswas, Enamul Hoque, Anock Somadder, Muhammad O. Faruk,
% Sharafuddin Md. Sharif, Nazia Chawdhury, Susanta K. Das, Yasmeen Haque, Nonlinear
% refractive index of 2, 5-Dimethylaniline in methanol by Z-scan technique, Journal of Optics
% (Accepted: http://link.springer.com/article/10.1007/s12596-014-0208-7).}
% \cvline{2.}{E. Hoque, A. Somadder, U. K. Mazumder, Y. Haque and S. K. Das, A DWBA Study of
% 60,62,64Ni($\alpha$, t)61,63,65Cu Reactions Using Different Optical Potentials, SUST Journal of Science
% and Technology, Vol. 21, P: 37 (2014).}
% \cvline{3.}{E. Hoque, M. K. Biswas, A. Somadder, M. O. Faruk, S. M. Sharif, N. Chawdhury, S. K. Das, Y.
% Haque, Nonlinear refractive index of Hibiscus Rosa-Sinensis by CW laser, Journal of Optics, Volume 42, Issue 3, pp 286-290 (2013).}
% \cvline{4.}{A. Somadder, E.Hoque, U.K. Mazumder, Y.Haque and S.K. Das, A DWBA study of the 48Ca($\alpha$,
% t)49Sc reaction using shallow (molecular), deep non-monotonic, Michel and normal optical
% potentials, Eur. Phys. J. A 49: 73 (2013).}
% \cvline{5.}{U. K. Mazumder, A. Somadder, E. Hoque, S. K. Das and H. M. Sen Gupta, 40Ca(6Li,d)44Ti
% Reaction and Effect of Three Potentials on the Spectroscopic Factors, SUST Journal of Science and
% Technology, Vol. 16, No.2 P:62-71 (2012).}
% 
% \subsection{Conference Articles}
% \cvline{1.}{Effective Contribution of Second Harmonic Generation in Nonlinear Optical Scattering, E.
% Haque, M. Das, M. K. Biswas, A. Somadder, M. O. Faruk, S. M. Sharif, N. Chawdhury, S. K. Das,
% Y. Haque, International Conference on Physics for Energy and Environment, Atomic Energy
% Centre, Dhaka, Bangladesh (06-08 March, 2014).}
% \cvline{2.}{Nonlinear Phase Shift and Refractive Index of 2,5 dimethyleaniline by the Modified Mach-
% Zehnder Interferometric Technique, M. Tasnim, K. Chakrabarty, M. K. Biswas, E. Haque, A.
% Somadder, M. O. Faruk, S. M. Sharif, N. Chawdhury, S. K. Das, Y. Haque, International
% Conference on Physics for Energy and Environment, Atomic Energy Centre, Dhaka, Bangladesh (06-08 March, 2014).}
% \cvline{3.}{Measurement of nonlinear refractive index of 2,5 di-methyl aniline (DMA) by z-scan technique
% using cw laser, P K Das, M. K. Biswas, E. Haque, A. Somadder, M. O. Faruk, S. M. Sharif, N.
% Chawdhury, S. K. Das, Y. Haque, International Conference on Advances in Physics 2013,
% Shahjalal University of Science and Technology, Sylhet, Bangladesh (03-05 January, 2013).}
% \cvline{4.}{Single beam z-scan for the calculation of n2 for poly dimethyle aniline, M. K. Biswas, E. Haque,
% A. Somadder, M. O. Faruk, S. M. Sharif, N. Chawdhury, S. K. Das, Y. Haque, International
% Conference on Advances in Physics 2013, Shahjalal University of Science and Technology, Sylhet,
% Bangladesh (03-05 January, 2013).}
% \cvline{5.}{ Theoretical Investigation of Solvent Effect on the Hyperpolarizability of Monomer and Dimer of DMA, Z. Abdullah, E. Haque, M. K. Biswas,
% A. Somadder, M. O. Faruk, S. M. Sharif, N. Chawdhury, S. K. Das, Y. Haque, International
% Conference on Advances in Physics 2013, Shahjalal University of Science and Technology, Sylhet,
% Bangladesh (03-05 January, 2013).}
% \cvline{6.}{ Measurement of Nonlinear Refractive Index with the Self-Action Method, M. R. Kader, E. Haque, M. K. Biswas,
% A. Somadder, M. O. Faruk, S. M. Sharif, N. Chawdhury, S. K. Das, Y. Haque, International
% Conference on Advances in Physics 2013, Shahjalal University of Science and Technology, Sylhet,
% Bangladesh (03-05 January, 2013).}
% \cvline{7.}{First Hyperpolarizability of 2, 5 dimethylaniline by Hyper Rayleigh Scattering Technique, M. A. T. Khan, U. K. Chowdhury, P. D. Tithi, E. Haque, M. K. Biswas,
% A. Somadder, M. O. Faruk, S. M. Sharif, N. Chawdhury, S. K. Das, Y. Haque, International
% Conference on Advances in Physics 2013, Shahjalal University of Science and Technology, Sylhet,
% Bangladesh (03-05 January, 2013).}
% \cvline{8.}{Estimation of Hyperpolarizability to the fundamental limit by Monte Carlo Simulation, E.
% Haque, M. K. Biswas, A. Somadder, M. O. Faruk, S. M. Sharif, N. Chawdhury, S. K. Das, Y.
% Haque, National Conference on Advances in Physics 2012, Shahjalal University of Science and
% Technology, Sylhet, Bangladesh (28-29 February, 2012).}
% \cvline{9.}{Nonlinear Optical Properties of Roselle Hibiscus by Z-Scan Technique, E.
% Haque, M. K. Biswas, A. Somadder, M. O. Faruk, S. M. Sharif, N. Chawdhury, S. K. Das, Y.
% Haque, National Conference on Advances in Physics 2012, Shahjalal University of Science and
% Technology, Sylhet, Bangladesh (28-29 February, 2012).}

\section{Seminars}
\cventry{June, 2013}{Enhancement of Second Harmonic Generation from Metallic Nanoparticles (Au, Ag and Pt)}{Department of Physics, Shahjalal University of Science and Technology}{Sylhet - 3114}{Bangladesh}{}

\section{Workshops and Trainings}
\subsection{Organized}
\cventry{Apr, 2014}{Python for Physicsts}{Computational Physics Laboratory}{Department of Physics, Shahjalal University of Science and Technology}{Sylhet - 3114, Bangladesh}{}
\subsection{Attended}
\cventry{Nov, 2014}{School on Parallel Programming and Parallel Architecture for HPC}{International Centre for Theoretical Physics}{Trieste, Italy}{}{}
\cventry{Mar, 2014}{Workshop on Advanced Techniques for Scientific Programming and Management of Open
Source Software Packages}{International Centre for Theoretical Physics}{Trieste, Italy}{}{}
\cventry{Jan, 2014}{Training on Teaching Methodology}{Shahjalal University of Science and Technology}{Sylhet - 3114, Bangladesh}{}{}
\cventry{Dec, 2013}{Workshop on Laser Operation Technique}{Research Laboratory: Nonlinear Optics}{Department of Physics, Shahjalal University of Science and Technology, Sylhet, Bangladesh}{}{}
\cventry{Oct, 2013}{Training on Simulink}{Matwork Private India, Ltd}{Pune, India}{}{}
\cventry{Oct, 2013}{Training on Matlab}{Matwork Private India, Ltd}{Pune, India}{}{}
\cventry{Feb, 2013}{Workshop on COMSOL Multi-Physics}{}{Dhaka, Bangladesh}{}{}
\cventry{Jan, 2012}{Workshop on Laser Fundamental}{Research Laboratory: Nonlinear Optics}{Department of
Physics, Shahjalal University of Science and Technology, Sylhet, Bangladesh}{}{}
\cventry{Jan, 2012}{Nonlinear Optics Research}{Research Laboratory: Nonlinear Optics}{Department of Physics,
Shahjalal University of Science and Technology, Sylhet, Bangladesh}{}{}

\section{Technical Experience}
\subsection{Proficient With}
\cvline{languages}{C, C++, Python, Multi-lang(Fortran, C and Python), Matlab, Mathematica, SigmaPlot, PHP, HTML, CSS}
\cvline{technologies}{Joomla CMS, MySQL, \LaTeX{}, Bash Scripting, Microsoft Office, Windows, Ubuntu, Mandriva}
\subsection{Have Experience With}
\cvline{languages}{Octave, Euler, Fortran}
\cvline{technologies}{Bash Scripting, pgplot, gnuplot, Drupal CMS, Git, Vim, Makefile, SQL Server, Visual Studio, Mac-OSX, Debian}
\subsection{Packages for Research}
\cvline{DWUCK}{This package have been used to find out the cross-sections in elastic scattering and nuclear reaction with various optical potential.}
\cvline{Others}{The Empire for calculating nuclear cross-sections, Comp-hep \& Yasara for Feynman reaction processes.}
\subsection{Developed Packages for Research}
\cvline{Z-scan}{Computational Package to obtain the result from the
experimental data of the Z-scan experiments and their analyses.}

\cvline{MCS}{Monte Carlo Simulation is coded in C++ to measure the fundamental
limit of the hyperpolarizability of nonlinear optical materials.}

\cvline{Others}{Dynamical behaviour of Smoke, Water flow in the base of small
depth, Eigenfunctions with Eigenvalues are practice (github) specially
concerning the Quantum Monte Carlo Simulation.}

\section{Languages}
\cvline{English}{Professionally Fluent}
\cvline{Bangla}{Mothertongue}

\section{Traveling}
\cvline{}{Raman Research Institute, Bengalore in India (2015)}
\cvline{}{Frankfurt and Koln in Germany ($9^{th}$ to $12^{th}$ November, 2014).}
\cvline{}{Trieste and Venice in Italy ($27^{th}$ October to $9^{th}$ November, 2014).}
\cvline{}{Trieste, Venice and Rome in Italy ($9^{th}$ to $25^{th}$ March, 2014).}
\cvline{}{Chennai, Bangalore, Goa, Pune, Kolkata in India ($28^{th}$ Sept to $14^{th}$ Oct, 2013).}

\section{Achievements}
\cvline{University}{I received scholarship $1^{st}$, $2^{nd}$ and $3^{rd}$ from my university of graduation.}
\cvline{College \& School}{I was rewarded as the best student of high school and college.}
\cvline{School}{I received the primary scholarship.}

\section{Activities}
\cvline{Current:}{Conducting research with both the Computational Physics Research Group (Professor Susanta Kumar Das) and the Nonlinear Optics Research Group (Professor Yasmeen Haque) at the Department of Physics, Shahjalal University of Science and Technology, Sylhet, Bangladesh.}

\cvline{University:}{I have acted as President of SAS (SUST Astronomical Society), I am the founder member of SDC (SUST Debating Club) and also SSA (SUST Science Arena). I was a member of the club KIN (a social welfare club).}
\cvline{College:}{I have acted as Secretary of Science Club and organized a Science Fair at the college. I was also a member of BNCC (Bangladesh National Cadet Corps).}
\cvline{School:}{I was the captain of the scout team at high school and I took part to serve the flood affected people with my scout team in 1998.}

\section{Hobbies}
\cvline{}{Different outdoor games like Football, Cricket and indoor games like Playing Card, Chess and Table Tennis are games of my choice.}
\cvline{}{I like to play Guitar and also watching movie is the best part of my entertainment for me.}
\cvline{}{Travelling through out the world is my passion and I also like to do photography.}

\section{Personal Information}
\cvline{Date of Birth}{$10^{th}$ September, 1984.}
\cvline{Nationality}{Bangladesh by Birth.}
\cvline{Marital Status}{Married.}

\section{Referees}
\cventry{}{Professor Yasmeen Haque}{Department of Physics, Shahjalal University
of Science and Technology}{Sylhet - 3114}{Bangladesh}{\url{yasmeen@sust.edu}}

\cventry{}{Professor Susanta Kumar Das}{Department of Physics, Shahjalal
University of Science and Technology}{Sylhet -
3114}{Bangladesh}{\url{skdas@siu.edu.bd}}
\end{document}
