%% start of file `template.tex'.
%% Copyright 2006-2010 Xavier Danaux (xdanaux@gmail.com).
%% Copyright 2010-2011 Mark Liu (markwayneliu@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[11pt,a4paper,sans]{moderncv}

\usepackage{verbatim}

% moderncv themes
\moderncvstyle{classic}
\moderncvcolor{blue}

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.8]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
%\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

\pagenumbering{latin}

% personal data
\firstname{}
\familyname{List of Publications}
%\address{Sabrina Bhaban, Sylhet - 3114, Bangladesh}{}    % optional, remove the line if not wanted
%\mobile{+880 1719 277759}                    % optional, remove the line if not wanted
%\email{mjonyh-phy@sust.edu}                      % optional, remove the line if not wanted
%\email{mjonyh@gmail.com}
%\homepage{https://sites.google.com/site/mjonyh}                % optional, remove the line if not wanted
%\extrainfo{\url{http://github.com/mjonyh}} % optional, remove the line if not wanted

% to show numerical labels in the bibliography; only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle
\textbf{Dr. Md. Enamul Hoque}

Assistant Professor, Department of Physics, SUST, Sylhet - 3114.
%\section{List of Publications}
\section{Journal Articles}
\cvline{1.}{\textbf{Md. Enamul Houqe}, Moushumi Das, Manash K. Biswas, Anock Somadder, Muhammad O Faurk, Sharif M. Sharafuddin, Nazia Chawdhury, Susanta K Das and Yasmeen Haque, \textit{Effect of dipolar and quadrupolar contribution in first hyperpolarizability of dimethylaniline}, Journal of Optics, Vol. 46, P: 37 (2017).}
\cvline{2.}{M. K. Biswas, P. K. Das, \textbf{E. Hoque}, S. M. Sharafuddin, S. K. Das and Y. Haque, \textit{Optical properties of benzene by the single thermal lens technique}, Journal of Nonlinear Optical Physics and Materials, Vol. 26, P: 1750025 (2017)}
\cvline{3.}{UK Mazumder, A Somadder, \textbf{E Hoque}, Y Haque, SK Das, HMS Gupta, \textit{Analysis of the normal optical, Michel and molecular potentials on the 40Ca(6Li, d)44 Ti reaction}, Pramana 86 (6), 1275-1286 (2016). }
\cvline{4.}{M. K. Biswas, \textbf{E. Hoque}, S. M. Sharif, S. K. Das and Y.  Haque, \textit{Single beam Z-scan for the calculation of nonlinear refractive index ($n_2$) for poly(2,5-dimethylaniline)}, Journal of Nonlinear Optical Physics and Materials, Vol. 24, P: 1550039 (2015)}
\cvline{5.}{MM Tasnim, K Chakrabarty, MK Biswas, E Hoque, SM Sharafuddin, Y Haque, \textit{Measurement of the nonlinear refractive index of 2, 5-dimethylaniline by a new technique using Mach–Zehnder interferometer}, Journal of Nonlinear Optical Physics \& Materials, Vol. 24, P: 1550004 (2015).}
\cvline{6.}{\textbf{E. Hoque}, A. Somadder, U. K. Mazumder, Y. Haque and S. K.  Das, \textit{A DWBA Study of 60,62,64Ni($\alpha$, t)61,63,65Cu Reactions Using Different Optical Potentials}, SUST Journal of Science and Technology, Vol. 21, P: 37 (2015).}
\cvline{7.}{M. M. Tasnim, K. Chakrabarty, M. K. Biswas, \textbf{E. Hoque}, S. M.  Sharafuddin, Y. Haque, \textit{Measurement of the nonlinear refractive index of 2, 5-dimethylaniline by a new technique using Mach–Zehnder interferometer}, Journal of Nonlinear Optical Physics and Materials, Vol. 24, P: 1550004 (2015)}
\cvline{8.}{Ponkog K. Das, Manash K. Biswas, \textbf{Enamul Hoque}, Anock Somadder, Muhammad O. Faruk, Sharafuddin Md. Sharif, Nazia Chawdhury, Susanta K. Das, Yasmeen Haque,\textit{Nonlinear refractive index of 2, 5-Dimethylaniline in methanol by Z-scan technique}, Journal of Optics, Vol.  44, P: 146 (2014)}
\cvline{9.}{\textbf{E. Hoque}, M. K. Biswas, A. Somadder, M. O. Faruk, S. M.  Sharif, N. Chawdhury, S. K. Das, Y. Haque, \textit{Nonlinear refractive index of Hibiscus Rosa-Sinensis by CW laser}, Journal of Optics, Vol. 42, P: 286 (2013).}
\cvline{10.}{A. Somadder, \textbf{E.Hoque}, U.K. Mazumder, Y.Haque and S.K. Das, \textit{A DWBA study of the 48Ca($\alpha$, t)49Sc reaction using shallow (molecular), deep non-monotonic, Michel and normal optical potentials}, Eur. Phys. J. A, Vol. 49, P: 73 (2013).}
\cvline{11.}{U. K. Mazumder, A. Somadder, \textbf{E. Hoque}, S. K. Das and H. M.  Sen Gupta, \textit{40Ca(6Li,d)44Ti Reaction and Effect of Three Potentials on the Spectroscopic Factors}, SUST Journal of Science and Technology, Vol. 16, No.2 P:62-71 (2012).}

\newpage

\section{Conference Articles}
\cvline{1.}{Numerical Analysis of Inverted pendulum Introduction, Mash-Huda Shipra, Khan Mahmud Enamul Hasan, Aakiful Islam, Md. Enamul Hoque, National Conference on Physics, University of Dhaka, (February 2019).}
\cvline{2.}{Numerical Analysis of the Dynamics of Two Charged Particles System, Shakir Ahmed, Mahiyath K Chowdhury, E. Hoque, National Conference on Physics, University of Dhaka, (February 2019).}
\cvline{3.}{Numerical Analysis of Fluid Flow by Navier-Stokes Equation, S M Shah Riyadh, E. Hoque, Susanta Kumar Das, 2nd INTERNATIONAL BOSE CONFERENCE - 2015, December 2015}
\cvline{4.}{The Runge-Kutta Method for Simulating a Dynamical System, E. Hoque, Jibril Ahammad, S. Halder, S. K. Das, National Conference on Physics Research and Education in BangladeshAt: Atomic Energy Centre, Dhaka, April 2015}
\cvline{5.}{Simulation of Thermal Steady State Time for Materials, E. Hoque, Md. Mahfuzzaman, Shamsad Tazmin, Susanta Kumar Das, National Conference on Physics Research and Education in BangladeshAt: Atomic Energy Centre, Dhaka, April 2015}
\cvline{6.}{Effective Contribution of Second Harmonic Generation in Nonlinear Optical Scattering, E.  Haque, M. Das, M. K. Biswas, A. Somadder, M. O. Faruk, S. M. Sharif, N. Chawdhury, S. K. Das, Y. Haque, International Conference on Physics for Energy and Environment, Atomic Energy Centre, Dhaka, Bangladesh (06-08 March, 2014).}
\cvline{7.}{Nonlinear Phase Shift and Refractive Index of 2,5 dimethyleaniline by the Modified Mach- Zehnder Interferometric Technique, M. Tasnim, K. Chakrabarty, M. K. Biswas, E. Haque, A.  Somadder, M. O. Faruk, S. M. Sharif, N. Chawdhury, S. K. Das, Y. Haque, International Conference on Physics for Energy and Environment, Atomic Energy Centre, Dhaka, Bangladesh (06-08 March, 2014).} 
\cvline{8.}{Measurement of nonlinear refractive index of 2,5 di-methyl aniline (DMA) by z-scan technique using cw laser, P K Das, M. K. Biswas, E. Haque, A. Somadder, M. O. Faruk, S. M. Sharif, N.  Chawdhury, S. K. Das, Y. Haque, International Conference on Advances in Physics 2013, Shahjalal University of Science and Technology, Sylhet, Bangladesh (03-05 January, 2013).}
\cvline{9.}{Single beam z-scan for the calculation of n2 for poly dimethyle aniline, M. K. Biswas, E. Haque, A. Somadder, M. O. Faruk, S. M. Sharif, N. Chawdhury, S. K. Das, Y. Haque, International Conference on Advances in Physics 2013, Shahjalal University of Science and Technology, Sylhet, Bangladesh (03-05 January, 2013).}
\cvline{10.}{Theoretical Investigation of Solvent Effect on the Hyperpolarizability of Monomer and Dimer of DMA, Z. Abdullah, E. Haque, M. K. Biswas, A. Somadder, M. O. Faruk, S. M. Sharif, N. Chawdhury, S. K. Das, Y. Haque, International Conference on Advances in Physics 2013, Shahjalal University of Science and Technology, Sylhet, Bangladesh (03-05 January, 2013).}
\cvline{11.}{Measurement of Nonlinear Refractive Index with the Self-Action Method, M. R. Kader, E. Haque, M. K. Biswas, A. Somadder, M. O. Faruk, S. M. Sharif, N. Chawdhury, S. K. Das, Y. Haque, International Conference on Advances in Physics 2013, Shahjalal University of Science and Technology, Sylhet, Bangladesh (03-05 January, 2013).}
\cvline{12.}{First Hyperpolarizability of 2, 5 dimethylaniline by Hyper Rayleigh Scattering Technique, M. A. T. Khan, U. K. Chowdhury, P. D. Tithi, E. Haque, M. K. Biswas, A. Somadder, M. O. Faruk, S. M. Sharif, N. Chawdhury, S. K. Das, Y. Haque, International Conference on Advances in Physics 2013, Shahjalal University of Science and Technology, Sylhet, Bangladesh (03-05 January, 2013).}
\cvline{13.}{Estimation of Hyperpolarizability to the fundamental limit by Monte Carlo Simulation, E.  Haque, M. K. Biswas, A. Somadder, M. O. Faruk, S. M. Sharif, N. Chawdhury, S. K. Das, Y.  Haque, National Conference on Advances in Physics 2012, Shahjalal University of Science and Technology, Sylhet, Bangladesh (28-29 February, 2012).}
\cvline{14.}{Nonlinear Optical Properties of Roselle Hibiscus by Z-Scan Technique, E.  Haque, M. K. Biswas, A. Somadder, M. O. Faruk, S. M. Sharif, N. Chawdhury, S. K. Das, Y.  Haque, National Conference on Advances in Physics 2012, Shahjalal University of Science and Technology, Sylhet, Bangladesh (28-29 February, 2012).}

\end{document}
